Some examples in extended logic counting classes

### 2016-04-06 tex/below.tex
6 abr

	\begin{algorithm}
		\caption{Calculate $\sp_M(x)$}
		\label{alg1}
		\begin{algorithmic}
			\REQUIRE $n \geq 0 \vee x \neq 0$
			\ENSURE $y = x^n$
			\STATE $y \leftarrow 1$
			\IF{$n < 0$}
			\STATE $X \leftarrow 1 / x$
			\STATE $N \leftarrow -n$
			\ELSE
			\STATE $X \leftarrow x$
			\STATE $N \leftarrow n$
			\ENDIF
			\WHILE{$N \neq 0$}
			\IF{$N$ is even}
			\STATE $X \leftarrow X \times X$
			\STATE $N \leftarrow N / 2$
			\ELSE[$N$ is odd]
			\STATE $y \leftarrow y \times X$
			\STATE $N \leftarrow N - 1$
			\ENDIF
			\ENDWHILE
		\end{algorithmic}
	\end{algorithm}

>>>>

	\begin{algorithm}

	\begin{algorithmic}[]
		\Begin
		\If{$f(x) = 0$} stop
		\Else \text{ choose from}
		\State stop
		\State call $\textsc{GenTree}_{f}(x,\{s_0\})$
		\EndIf
		\EndBegin
		\Procedure{$\textsc{GenTree}_{f}(x,S)$}{}
		\State $S_0 = \emptyset$, $S_1 = \emptyset$
		\For{$s\in S$}
		\State do a search in the configuration graph of $M$ with input $x$ from $s$:
		\If{$s'$ is reached after writing 0 in the output tape} $S_0 \gets s'$
		\EndIf
		\If{$s'$ is reached after writing 1 in the output tape} $S_1 \gets s'$
		\EndIf
		\EndFor
		\If{a final state from $M$ is reachable from some $s\in S_0$ and some $s'\in S_1$} choose between:
		\State call $\textsc{GenTree}_{f}(x,S_0)$
		\State call $\textsc{GenTree}_{f}(x,S_1)$
		\ElsIf{a final state from $M$ is reachable from some $s\in S_i$ but not from any $s'\in S_{1-i}$}
		\State call $\textsc{GenTree}_{f}(x,S_0)$
		\ElsIf{no final state from $M$ is reachable from any $s\in S_0 \cup S_1$}
		\State stop
		\EndIf
		\EndProcedure
	\end{algorithmic}

	\end{algorithm}

	We use $s_0$ for the initial state of $M$ with input $x$. The algorithm can be executed in a nondeterministic polynomial-time machine, so we only need to show that the number of computation paths is equal to $\sp_M(x)$.
